SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-05-08 Chapters/Chapter02.tex
SDM Reinforcement learning citations and minor fixes.
sdm

% TODO GARY KLEIN !!!

@@

Sparse Distributed Memory reads like a \emph{desiderata} of a theory for human memory.  To understand the breadth of topics that SDM encompasses, consider the following questions:
\begin{enumerate}
    \item Why are most concepts orthogonal, unrelated to each other?
    \item Why is there Miller's magic number, i.e., we can't hold too many things in mind at once?
    \item Why do we at times instantly recall an experience; other times we can't recall anything at all; and still other times we get into this strange tip-of-the-tongue situation... it is clearly `there'... but where?  (and `what' is `there'?\footnote{Psychologists have documented interesting properties about this state:  it happens, for instance, around every 1-week cycle; and it happens mostly over proper names, subjects have access to the first letter and to the number of syllables better than chance, etc. Also interesting is their clever way of triggerring the state: through definitions of rarely-used words.  For some psychological studies about the tip-of-tongue, see \citet{meyer_tip---tongue_1992, brown_review_1991, brown_tip_1966}.}.)
    \item How does this recall process work?  What is remembering?
    \item Why do neurons die and we still remember most everything?
    \item What do neurons actually do?  What is their primary function?
\end{enumerate}

@@

I have run the classification algorithm under the MNIST database of handwritten digits \citep{deng2012mnist}. First, SDM has been trained with the 60,000 training images, and then it classified the 10,000 testing images. In these initial tests, the memory has given the correct classification for 79.22\% of the images, which is inferior to the specialized algorithms. For instance, in 1998, \citet{lecun1998gradient} have developed algorithms which achieve from 88\% through a linear classifier, to 99.7\% through a convolutional net. For a review of algorithms' performance in the MNIST database, see \cite{mnist}.

>>>>

@@

Sparse Distributed Memory reads like a \emph{desiderata} of a theory for human long-term memory.  To understand the breadth of topics that SDM encompasses, consider the following questions:
\begin{enumerate}
    \item Why are most concepts orthogonal, unrelated to each other?
    \item Why is there Miller's magic number, i.e., we can't hold too many things in mind at once?
    \item Why do we at times instantly recall an experience; other times we can't recall anything at all; and still other times we get into this strange tip-of-the-tongue situation... it is clearly `there'... but where?  (and `what' is `there'?\footnote{Psychologists have documented interesting properties about this state:  it happens, for instance, around every 1-week cycle; and it happens mostly over proper names, subjects have access to the first letter and to the number of syllables better than chance, etc. Also interesting is their clever way of triggerring the state: through definitions of rarely-used words.  For some psychological studies about the tip-of-tongue, see \citet{meyer_tip---tongue_1992, brown_review_1991, brown_tip_1966}.}.)
    \item How does this recall process work?  What is remembering?
    \item Why do neurons die and we still remember most everything?
    \item What do neurons actually do?  What is their primary function?
\end{enumerate}

@@

I have run the classification algorithm under the MNIST database of handwritten digits \citep{deng2012mnist}. First, SDM has been trained with the 60,000 training images, and then it classified the 10,000 testing images. In these initial tests, the memory has given the correct classification for 79.22\% of the images, which is inferior to the specialized algorithms. For instance, in 1998, \citet{lecun1998gradient} have developed algorithms which achieve from 88\% through a linear classifier, to 99.7\% through a convolutional net. For a review of algorithms' performance in the MNIST database, see \cite{deng2012mnist}.
